A Stopped Negative Binomial Distribution

### 2016-02-29 stat-and-prob-letters/snb-paper.tex
yeah.

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{url}
\DeclareMathOperator*{\argmin}{argmin}
\newcommand*{\argminl}{\argmin\limits}
\newtheorem{prop}{Proposition}

@@

The probability mass function of $\,Y\,$ has a variety of shapes for different 
choices of the parameters $(s,\, t,\,p)$.  These shapes are illustrated in 
Fig.~\ref{shapes.fig}. The SNB is related to the negative binomial 
distribution. Specifically, if $t$ is large then the $Y-s$ has a negative 
binomial distribution with
\begin{equation*}                                    %   (1)   
\mathbb{P}[Y=s+j]        \label{nb1.eq}          
  = {{s+j-1}\choose{s-1}} p^s (1-p)^j
\end{equation*}
for $\,j=0, 1,\ldots\,$. A similar statement can be made when $s$ is large
and $t$ is small.

For the special case of $\,s=t,$ the distribution of $\,Y\,$ is the
riff-shuffle, or minimum negative binomial distribution~\citep{Uppuluri1970}.
Similar derivations of the closely-related maximum negative binomial 
discrete distributions also appear in~\cite{Zhang2000}
and \cite{Zelterman2005}.
The maximum negative binomial is the smallest number of outcomes necessary to 
observe at least $c$ successes {\em and} $c$ failures, but the SNB givethe 
number of coin flips to observe {\em either} $s$ heads or $t$ tails.

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{url}
\usepackage{subfig}
\DeclareMathOperator*{\argmin}{argmin}
\newcommand*{\argminl}{\argmin\limits}
\newtheorem{prop}{Proposition}

@@

The SNB is related to the negative 
binomial distribution. Specifically, if $t$ is large then the $Y-s$ has a 
negative binomial distribution with
\begin{equation*}                                    %   (1)   
\mathbb{P}[Y=s+j]        \label{nb1.eq}          
  = {{s+j-1}\choose{s-1}} p^s (1-p)^j
\end{equation*}
for $\,j=0, 1,\ldots\,$. A similar statement can be made when $s$ is large
and $t$ is small. As a result, with proper parameter choice, the SNB
can mimic other probability distributions in a manner similar to 
that described in \cite{Peizer1968} and \cite{Best1974}. Examples are
shown in in Fig.~\ref{shapes.fig}.

For the special case of $\,s=t,$ the distribution of $\,Y\,$ is the
riff-shuffle, or minimum negative binomial distribution~\citep{Uppuluri1970}.
Similar derivations of the closely-related maximum negative binomial 
discrete distributions also appear in~\cite{Zhang2000}
and \cite{Zelterman2005}.
The maximum negative binomial is the smallest number of outcomes necessary to 
observe at least $c$ successes {\em and} $c$ failures. The SNB is the 
number of coin flips to observe {\em either} $s$ heads or $t$ tails.

@@

\begin{figure}[t!]
\centering
\subfloat[The SNB distribution.]{\includegraphics[width=0.5\textwidth]{snb_density.pdf}}
\hfill
\subfloat[The Binomial distribution.]{\includegraphics[width=0.5\textwidth]{bin_density.pdf}}
\caption{
SNB(0.2, 2, 12) with mass contributed from 
$s$ successes (red) or $t$ failures (teal) along with Bin(0.2, 13) with
at least 2 successes (red) or fewer (teal).
}
\label{fig:kane_viz}
\end{figure}
